From Likes to Change: Assessing the Impact of Citizen Engagement on the European

### 2023-06-14 Article.Rmd
Articol final modificat

---
title: 'From Likes to Change: Assessing the Impact of Citizen Engagement on the European
  Commission''s Social Media Platforms'
author:
- name: Tanase Tasențe
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: "tanase.tasente@365.univ-ovidius.ro"
  role:
  - Equal contribution
  - Conceptualization
  - Data curation
  - Investigation
  - Formal analysis
  - Resources
  - Software
  - Visualization
  - "Writing - Original Draft Preparation"
  - "Writing - Review & Editing"
- name: "Cristian Opariuc-Dan"
  affiliation: '1,2'
  role:
  - Equal contribution
  - "Writing - Original Draft Preparation"
  - "Writing - Review & Editing"
  - Data curation
  - Formal analysis
  - Resources
  - Software
  - Visualization
- name: Cristina Dana Popescu
  affiliation: '1'
  role:
  - "Writing - Original Draft Preparation"
  - "Writing - Review & Editing"
  - Professional proofreading
shorttitle: Impact of Citizen Engagement on the European Commission's Social Media
  Platforms
output:
  pdf_document: papaja::apa6_pdf
  word_document: papaja::apa6_docx
  html_document:
    df_print: paged
authornote: |
  Department of Administrative and Social Sciences
abstract: "This study investigates the role of emotional resonance in social media
  communications from the European Commission (EC) and its impact on public participation
  across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings
  indicate that emotionally resonant communications significantly enhance public engagement,
  with variations depending on the specific platform. Both positive and negative emotional
  resonance significantly impact participation, with the latter having a more pronounced
  effect. Our research highlights the critical importance of platform-specific strategies
  and the incorporation of emotional resonance in public communications to foster
  participation in policy dialogues. An analysis of the engagement rates and sentiment
  across platforms reveals unique tonal variations in the EC's discourse. The effect
  of emotional resonance on public engagement is also found to be moderated by the
  choice of social media platform, with certain platforms more significantly moderating
  the relationship between emotional resonance and engagement than others. This study
  lays the groundwork for refining communication strategies within a multi-platform
  digital governance environment.\n"
keywords: "social media, public institutions, emotional resonance, public engagement,
  platform-specific strategies, digital governance"
wordcount: 4067 words in text body 1034 words in reference section
bibliography:
- "r-references.bib"
- references.bib
floatsintext: no
linenumbers: yes
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
documentclass: apa7
classoption: man
csl: apa.csl
affiliation:
- id: '1'
  institution: Ovidius University of Constanța, Romania
- id: '2'
  institution: University of Bucharest, Romania
header-includes: \usepackage{ragged2e}
---

```{r setup, include = FALSE}
  library(papaja); library(knitr); library(readxl); library(dplyr); library(psych)
  library(sasLM);library(rstatix); library(naniar); library(lubridate); library(flextable)
  library(caret); library(ggpubr); library(lm.beta); library(relaimpo); library(nortest)
  library(interactions); library(misty); library(tm); library(SentimentAnalysis); library(ggplot2)

  r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
  set.seed(44542)
  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Introduction
\justify
In recent years, the rise of social media platforms has led to significant changes in the way institutions, including public organizations, communicate with their audiences. As a result, the importance of citizen engagement in the process of communication through social media has become increasingly recognized. This engagement involves not only a one-way flow of information from public institutions to citizens, but also an interactive dialogue between the two parties.

>>>>

---
title             : "From Likes to Change: Assessing the Impact of Citizen Engagement on the European Commission's Social Media Platforms"
shorttitle: "Impact of Citizen Engagement on the European Commission's Social Media Platforms"
author            :
- name            : "Tanase Tasențe"
  affiliation     : '1'
  corresponding   : yes
  address         : "Aleea Universității"
  email           : "tanase.tasente@365.univ-ovidius.ro"
  role            :
    - "Equal contribution"
    - "Conceptualization"
    - "Data curation"
    - "Investigation"
    - "Formal analysis"
    - "Resources"
    - "Software"
    - "Visualization"
    - "Writing - Original Draft Preparation"
    - "Writing - Review & Editing"
- name            : "Cristian Opariuc-Dan"
  affiliation     : '1,2'
  role            :
    - "Equal contribution"
    - "Writing - Original Draft Preparation"
    - "Writing - Review & Editing"
    - "Data curation"
    - "Formal analysis"
    - "Resources"
    - "Software"
    - "Visualization"
- name            : "Cristina Dana Popescu"
  affiliation     : '1'
  role            :
    - "Writing - Original Draft Preparation"
    - "Writing - Review & Editing"
    - "Professional proofreading"
affiliation     :
  - id          : '1'
    institution : "Ovidius University of Constanța, Romania"
  - id          : '2'
    institution : "University of Bucharest, Romania"
authornote: |

  Tanase Tasente (Orcid ID: https://orcid.org/0000-0002-3164-5894) is a lecturer and ERASMUS coordinator at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta. He holds a bachelor's, master's, and doctoral degree in Communication Sciences and a master's degree in European Administration, Institutions, and Public Policies. With over 100 published scientific papers and 4 authored books on institutional communication through social media and public policy strategies, the author has made significant contributions to the academic community. Additionally, he is the director of two international public relations companies, Plus Communication and International Communication & PR, where they have overseen marketing, advertising, and public relations campaigns for renowned multinational companies. His combination of academic and professional experience has equipped them with the necessary skills and knowledge to excel in various fields of communication and administration.
  Cristian Opariuc-Dan (Orcid ID: https://orcid.org/0000-0003-4079-0142) is a lecturer at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta. He holds a Bachelor's degree in Psychology, a Master's degree in Administrative Sciences, and a PhD in Psychology. He serves as the coordinator of the Law and Public Administration programs (part-time education) at Ovidius University and is an associate professor in the Doctoral Schools of Psychology and Education Sciences at the University of Bucharest and "Al. I. Cuza" University in Iasi. With over 50 scientific articles published in specialized journals and as the author and co-author of 5 books in the field of statistics and data analysis, he has demonstrated his expertise in the academic field.
abstract: |
  This study investigates the role of emotional resonance in social media  communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings  indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform. Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced  effect. Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues. An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse. The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others. This study lays the groundwork for refining communication strategies within a multi-platform   digital governance environment.

keywords        : "social media, public institutions, emotional resonance, public engagement, platform-specific strategies, digital governance"
wordcount       : "4275 words in text body 1034 words in reference section"
bibliography    : ["r-references.bib", "references.bib"]
floatsintext    : no
linenumbers     : yes
draft           : no
mask            : no
figurelist      : no
tablelist       : no
footnotelist    : no
documentclass   : "apa7"
classoption     : "man"
csl             : apa.csl
header-includes : \usepackage{ragged2e}
output          :
  pdf_document  : papaja::apa6_pdf
  html_document :
    df_print    : paged
  word_document : papaja::apa6_docx
---

```{r setup, include = FALSE, echo=FALSE}
  library(papaja); library(knitr); library(readxl); library(dplyr); library(psych)
  library(sasLM);library(rstatix); library(naniar); library(lubridate); library(flextable)
  library(caret); library(ggpubr); library(lm.beta); library(relaimpo); library(nortest)
  library(interactions); library(misty); library(tm); library(SentimentAnalysis); library(ggplot2)
  r_refs("r-references.bib")
```

```{r analysis-preferences, echo=FALSE}
# Seed for random number generation
  set.seed(44542)
  knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Introduction
\justify
In recent years, the rise of social media platforms has led to significant changes in the way institutions, including public organizations, communicate with their audiences. As a result, the importance of citizen engagement in the process of communication through social media has become increasingly recognized. This engagement involves not only a one-way flow of information from public institutions to citizens, but also an interactive dialogue between the two parties.
